A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2021-02-01 01_TrialsForInclusionInAnalysis.Rmd
correct yield variance calculation

### Yield variance standardisation
```{r StandardiseYieldVariance}
PM_MB_dat <-
   PM_MB_dat %>%
   mutate(
      vi =
         case_when(
            Y_error_type == "stdev" ~ disease_error ^ 2,
            Y_error_type == "lsd (P=0.05)" ~
               (replicates * ((disease_error / 1.96) ^ 2) / 2) / replicates
         ),
      spray_management = fct_relevel(spray_management, sort)
   ) %>%
   select(-c(yield_error,
             Y_error_type))

>>>>

### Yield variance standardisation
```{r StandardiseYieldVariance}
PM_MB_dat <-
   PM_MB_dat %>%
   mutate(
      vi =
         case_when(
            Y_error_type == "stdev" ~ yield_error ^ 2,
            Y_error_type == "lsd (P=0.05)" ~
               (replicates * ((yield_error / 1.96) ^ 2) / 2) / replicates
         ),
      spray_management = fct_relevel(spray_management, sort)
   ) %>%
   select(-c(yield_error,
             Y_error_type))
